Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex

There are two approaches for the {\sc verify} phase based on the
described model.  The first uses interval arithmetic \cite{moore1966interval}
to represent the coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
and rounds operations outwards during calculations. 
%\cdsay{dario, what coefficients are these?}
% This results in a
% tighter calculation of the error at the cost of
% performance.
Synthesised controllers using this verifier will always
be correct and only generate counterexamples when the precision of the
engine is insufficient. Given the high computational cost of this
approach, we also designed a second approach, which we describe below.
Our experimental results described in Sec.~\ref{sec:experiments},  
%try both approaches and provide the time for the fastest. 
show that the increase in speed of the second approach 
over the first one is in most cases of several orders of magnitude.

In Fig.~\ref{fig:CEGIS}, we illustrate the second approach, which 
uses a two-stage verification such that in the first stage we 
assume a certain precision \param{I_b}{F_b}  
followed by checking the soundness of our assumption
in a second verification stage.

>>>>

There are two approaches for the {\sc verify} phase.
% based on the described model.  
The first uses interval arithmetic \cite{moore1966interval}
to represent the coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
and rounds operations outwards during calculations. 
%\cdsay{dario, what coefficients are these?}
% This results in a
% tighter calculation of the error at the cost of
% performance.
Synthesised controllers using this verifier will always
be correct and only generate counterexamples when the precision of the
engine is insufficient. Given the high computational cost of this
approach, we also designed a second approach, which we describe below.
Our experimental results described in Sec.~\ref{sec:experiments},  
%try both approaches and provide the time for the fastest. 
show that the increase in speed of the second approach 
over the first one is in most cases of several orders of magnitude.

The second approach is illustrated in Fig.~\ref{fig:CEGIS} and 
uses a two-stage verification such that in the first stage we 
assume a certain precision \param{I_b}{F_b}  
followed by checking the soundness of our assumption
in a second verification stage.
